---
title: "Stat 412"
author: "Yolanda Jin"
date: "24/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## EDA

- Might need to filter out NA data 

- monthly income = 0

- 30k monthly income = NA

- # Dependent = NA 4k

- age 0 remove - only 1 point

- age very old

- group by age group etc

- 13 - 101 or older (maybe cut at 100)

- 80 or more


## Question

Comparing our model against paper's model

- Most important factors


## Ensemble Learning

- Lasso Ensemble Algorithm

- Aggregating base learner: Weighted base=learner


## Balancing Data

- Use clustering and pick one sub-group from majority

- Use bagging algorithm to create more minority data

- Use NA indicator 0 or 1 (maybe use mean/median)


## Which models to try

- Logistic regression (compare the different link functions)

- look maybe merge Lasso with logistic regression

- RF

## Evaluating Model/Comparing results

- AUC



```{r echo=FALSE}

```

